Portfolios of Subgraph Isomorphism Algorithms

### 2015-12-16 paper/paper.tex
A bit of consistency in cite styles

\paragraph{Overview of the paper.}
We formally define the subgraph isomorphism problem in Section~\ref{sec:defs}. 
In Section~\ref{sec:algs}, we describe the main existing algorithms for solving this problem, and we also introduce two new algorithms which are derived from the LAD algorithm of~\cite{Solnon:2010}.

In Section~\ref{sec:algs}, we experimentally compare eight state-of-the-art
algorithms. We introduce a large benchmark set composed of 5725 instances
composed of twelve classes. Ten of these classes have been introduced in the
experimental study reported in~\cite{McCreesh:2015}. We evaluate the algorithms,
of which two are novel, on this benchmark set, and show that they have very
complementary performance. In particular, we show that depending on the CPU time
limit, different algorithms achieve the best performance on the entire benchmark
set.

>>>>

\paragraph{Overview of the paper.}
We formally define the subgraph isomorphism problem in Section~\ref{sec:defs}.
In Section~\ref{sec:algs}, we describe the main existing algorithms for solving
this problem, and we also introduce two new algorithms which are derived from
Solnon's \LAD algorithm \cite{Solnon:2010}.

In Section~\ref{sec:algs}, we experimentally compare eight state-of-the-art
algorithms. We introduce a large benchmark set composed of 5725 instances
composed of twelve classes. Ten of these classes have been introduced in the
experimental study reported by McCreesh and Prosser~\cite{McCreesh:2015}. We
evaluate the algorithms, of which two are novel, on this benchmark set, and
show that they have very complementary performance. In particular, we show that
depending on the CPU time limit, different algorithms achieve the best
performance on the entire benchmark set.
